Supplementary Information

### 2020-10-09 writing/transect_supplement.Rmd
specify samples sizes explicitly to clean up low-sample values on accumulation curves, and move OTU curve to supplement.
reword distance decay table legend
Auto stash before merge of "master" and "origin/master"

```{r buffer-compare-long, fig.scap = "(ref:buffer-compare-long-s)", fig.cap = "(ref:buffer-compare-long-s). (ref:buffer-compare-long)", fig.width = 5, fig.height = 5, out.width = "100%", cache = TRUE, extra.cache = gethash("buffer_compare_long")}
oldtheme <- theme_update(panel.border = element_blank())
readd(buffer_compare_long)
theme_set(oldtheme)
```

@@

```{r buffer-compare-short, fig.scap="(ref:buffer-compare-short-s)", fig.cap = "(ref:buffer-compare-short-s). (ref:buffer-compare-short)", fig.width = 5, fig.height = 5, out.width = "100%", cache = TRUE, extra.cache = gethash("buffer_compare_short")}
oldtheme <- theme_update(panel.border = element_blank())
readd(buffer_compare_short)
theme_set(oldtheme)

@@

@@

```{r correlog, fig.cap="(ref:correlog-cap-s). (ref:correlog-cap)", fig.scap = "(ref:correlog-cap-s)", cache=TRUE, extra.cache=gethash(as.list(keep(light_plan$target, startsWith, "correlog")))}
light_plan %>%
  filter(startsWith(target, "correlog")) %>%
  select(target) %>%
  separate(
    target,
    into = c("step", "guild", "metric", "tech", "amplicon", "method", "tdist"),
    sep = "_",
    remove = FALSE
  ) %>%
  filter(startsWith(method, "PHYLOTAX")) %>%
  mutate(
    tdist = paste(tdist, "year"),
    guild = plyr::mapvalues(guild, c("fungi", "ecm"), c("all Fungi", "ECM")),
    metric = plyr::mapvalues(metric, c("bray", "wunifrac"), c("Bray-Curtis", "W-UNIFRAC")),
    amplicon = factor(amplicon, levels = c("Short", "Long"))
  ) %>%
  mutate_at("target", purrr::map, readd, character_only = TRUE) %>%
  mutate_at("target", purrr::map, "mantel.res") %>%
  mutate_at("target", purrr::map, as.data.frame) %>%
  unnest(target) %>%
  filter(complete.cases(.)) %>%
  mutate(Significant = `Pr(corrected)` < 0.05) %>%
  ggplot(aes(class.index, Mantel.cor, group = tdist, color = tdist, shape = Significant)) +
  geom_point(size = 3) +
  geom_line(alpha = 0.3, size = 1.5) +
  geom_hline(yintercept = 0, linetype = 2, alpha = 0.5) +
  # geom_line(aes(y = exp(predict(bc_fit)))) +
  scale_y_continuous(name = "Mantel correlation") +
  scale_x_continuous(breaks = c(0, 3, 6, 9, 12)) +
  scale_color_discrete(name = "Time lag") +
  xlab("Distance (m)") +
  ggnomics::facet_nested(amplicon + tech + metric ~ guild, scales = "fixed", nest_line = TRUE) +
  scale_shape_manual(values = c("TRUE" = 16, "FALSE" = 1)) +
  theme(strip.background = element_blank())
```

@@

(ref:variofit) Parameters for exponential distance-decay fits. Range: range at which exponential function is at 95% of its maximum value.

>>>>

```{r buffer-compare-long, fig.scap = "(ref:buffer-compare-long-s)", fig.cap = "(ref:buffer-compare-long-s). (ref:buffer-compare-long)", fig.width = 10, fig.height = 10, out.width = "100%", cache = TRUE, extra.cache = gethash("buffer_compare_long"), dev = "pdf"}
oldtheme <- theme_update(panel.border = element_blank())
readd(buffer_compare_long)
theme_set(oldtheme)
```

@@

```{r buffer-compare-short, fig.scap="(ref:buffer-compare-short-s)", fig.cap = "(ref:buffer-compare-short-s). (ref:buffer-compare-short)", fig.width = 10, fig.height = 10, out.width = "100%", cache = TRUE, extra.cache = gethash("buffer_compare_short"), dev = "pdf"}
oldtheme <- theme_update(panel.border = element_blank())
readd(buffer_compare_short)
theme_set(oldtheme)

@@

```{r accum-OTU, fig.cap="OTU accumulation curves"}
readd(accum_plot_OTU)
```

@@

```{r correlog, fig.cap="(ref:correlog-cap-s). (ref:correlog-cap)", fig.scap = "(ref:correlog-cap-s)", cache=TRUE, extra.cache=gethash(as.list(purrr::keep(light_plan$target, stringr::str_detect, "^correlog.+_PHYLOTAX_")))}
light_plan %>%
  filter(startsWith(target, "correlog")) %>%
  select(target) %>%
  separate(
    target,
    into = c("step", "guild", "metric", "tech", "amplicon", "method", "tdist"),
    sep = "_",
    remove = FALSE
  ) %>%
  filter(startsWith(method, "PHYLOTAX")) %>%
  mutate(
    tdist = paste(tdist, "year"),
    guild = plyr::mapvalues(guild, c("fungi", "ecm"), c("all Fungi", "ECM")),
    metric = plyr::mapvalues(metric, c("bray", "wunifrac"), c("Bray-Curtis", "W-UNIFRAC")),
    amplicon = factor(amplicon, levels = c("Short", "Long"))
  ) %>%
  mutate_at("target", purrr::map, readd, character_only = TRUE) %>%
  mutate_at("target", purrr::map, "mantel.res") %>%
  mutate_at("target", purrr::map, as.data.frame) %>%
  unnest(target) %>%
  filter(complete.cases(.)) %>%
  mutate(Significant = `Pr(corrected)` < 0.05) %>%
  ggplot(aes(class.index, Mantel.cor, group = tdist, color = tdist, shape = Significant)) +
  geom_point(size = 3) +
  geom_line(alpha = 0.3, size = 1.5) +
  geom_hline(yintercept = 0, linetype = 2, alpha = 0.5) +
  # geom_line(aes(y = exp(predict(bc_fit)))) +
  scale_y_continuous(name = "Mantel correlation") +
  scale_x_continuous(breaks = c(0, 3, 6, 9, 12)) +
  scale_color_discrete(name = "Time lag") +
  xlab("Distance (m)") +
  ggnomics::facet_nested(amplicon + tech + metric ~ guild, scales = "fixed", nest_line = TRUE) +
  scale_shape_manual(values = c("TRUE" = 16, "FALSE" = 1)) +
  theme(strip.background = element_blank())
```

@@

(ref:variofit) Parameters for exponential distance-decay fits. Range: range at which exponential function is at 95% of its asymptotic value.
